GPU Acceleration of Machine Learning-Aided Facial Recognition and Edge-Based Motion Detection with NVIDIA CUDA

### 2015-12-11 documents/paper/paper.tex
Edge-based motion detection block diagram

\subsection{GPU Computation and the NVIDIA CUDA Framework}
Formally, NVIDIA CUDA is a parallel computing platform and programming model that exposes familiar C-based APIs for parallelized computations. CUDA is NVIDIA's platform for general-purpose computing on graphics processing units (commonly, GPGPU or GP$^2$U), or the use of a GPU for computations traditionally handled by the CPU. Generally, GPGPU is used to exploit the improved multithreaded performance and raw floating-point computational ability of GPUs over CPUs. For example, on modern hardware, an NVIDIA GeForce GTX 970 (1664 CUDA cores) exhibits peak single-precision floating point performance of nearly 3500 GFLOPS (floating-point operations per second), while an Intel Core i7 4790K (4C, 8T) achieves 100 GFLOPS. Our goal is to demonstrate the performance of GPU computing by solving a handful of existing problems in computer vision with CUDA: namely, edge detection and motion detection.

@@

>>>>

\subsection{GPU Computation and the NVIDIA CUDA Framework}
Formally, CUDA (Compute Unified Device Architecture) is a parallel computing platform and programming model that exposes familiar C-based APIs for parallelized computations. CUDA is NVIDIA's platform for general-purpose computing on graphics processing units (commonly, GPGPU or GP$^2$U), or the use of a GPU for computations traditionally handled by the CPU. Generally, GPGPU is used to exploit the improved multithreaded performance and raw floating-point computational ability of GPUs over CPUs. For example, on modern hardware, an NVIDIA GeForce GTX 970 (1664 CUDA cores) exhibits peak single-precision floating point performance of nearly 3500 GFLOPS (floating-point operations per second), while an Intel Core i7 4790K (4C, 8T) achieves 100 GFLOPS. Our goal is to demonstrate the performance of GPU computing by solving a handful of existing problems in computer vision with CUDA: namely, edge detection and motion detection.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.8\textwidth]{high_level_block_diagram.png}
	\caption{High-level block diagram describing our implementation of a real-time edge-based motion detector}
	\label{motion-detection-block-diagram}
\end{figure*}
